Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-11 article.tex
add values for inverse correlation (pr)

\begin{table}[htb]
\centering
\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & & & & \\
PCA                 & & & & \\
Weights             & & & & \\
Weights + PCA       & & & & \\
H-T                 & & & & \\
H-T + PCA           & & & & \\
H-T + Weights       & & & & \\
H-T + Weights + PCA & & & & \\
PCA                 & & & & \\
P-P + PCA           & & & & \\
P-P + Weights       & & & & \\
P-P + Weights + PCA & & & & \\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[htb]
\centering
\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
PCA                 & 0.322 & 0.324 & 0.323 & 0.312\\
P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}
